### 2024-04-22 scripts/02-data_cleaning.qmd
clean
delete duplicated data

# Code referenced from:https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html

raw_pockets_data<-
  read_csv(
    file = here::here("data/raw_data/raw_pockets_data.csv"),
    show_col_types = FALSE
  )

# Change the name of the raw data into the clean data
cleaned_pockets_data <-
  clean_names(raw_pockets_data)

# Select the rows of interest
cleaned_pockets_data <-
  cleaned_pockets_data |>
  select(
    brand,
    style,
    men_women,
    price
  )

cleaned_pockets_data

@@

# Select the rows of interest
cleaned_area_data <-
  cleaned_area_data |>
  select(
    brand,
    style,
    men_women,
    pocket_area,
    price,
  )

cleaned_area_data
```

```{r}
#### Save cleaned data ####
# Code referenced from:https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html

# save cleaned pockets data 
write_csv(
  x = cleaned_pockets_data,
  file = here::here("data/analysis_data/cleaned_pockets_data.csv")
)

# save json cleaned data (pocket area measurements)

>>>>

@@

# Select the rows of interest
cleaned_area_data <-
  cleaned_area_data |>
  select(
    brand,
    men_women,
    price,
    pocket_area,
  )

cleaned_area_data

```

```{r}
#### Save cleaned data ####
# save json cleaned data (pocket area measurements)
